Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-10-31 paper.tex
Added application table

\documentclass{article}
\usepackage{minted}
\usepackage{pdfcomment}
\usepackage[margin=1in]{geometry}

@@

@@

@@

A table summarizing which Boutiques features are used in which pipelines.

\begin{tabular}{ccccccccccccc}
  Application & \multicolumn{3}{c}{Containers} & \multicolumn{7}{c}{Input/Output properties}                         & \multicolumn{2}{c}{Other properties}  \\
              & Docker & Singularity & Rootfs  & Dependencies & Groups & Lists & Optional & Default & Enum & Min/max & Env vars & Min/Max \\

PSOM & 
\end{tabular}

>>>>

\documentclass{article}
\usepackage{minted}
\usepackage{pdfcomment}
\usepackage[margin=1in]{geometry}
\usepackage{lscape}
\usepackage[table]{xcolor}

@@

Containers are not mandatory though. If an application manifest does
not contain any reference to a container, the platform will assume
that the application is pre-installed on the execution infrastructure.

@@

New list mechanism.

@@

Table~\ref{table:applications} summarizes the applications described
with Boutiques and the main features used.
\begin{landscape}
  \begin{table}
  \rowcolors{2}{gray!25}{white}
  \begin{tabular}{l|ccc|ccccccc|cc}
    Application               &\multicolumn{3}{c|}{Containers} & \multicolumn{7}{c|}{Input/Output properties}                         & \multicolumn{2}{c}{Other properties}  \\
                              &Docker              & Singularity & Rootfs  & Dependencies      &Groups             & Lists             & Optional          &Default            & Enum              & Min/max           & Config. file & Env vars     \\
    \hline
    Niak pre-processing       &\cellcolor{gray!75} &            &         &                   &\cellcolor{gray!75}&                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&              &\cellcolor{gray!75}\\
    ICA AROMA                 &\cellcolor{gray!75} &            &         &\cellcolor{gray!75}&\cellcolor{gray!75}&                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&              &\\
    FSL tools &&&&&&&&&&&&\\
    \multicolumn{1}{r|}{anat} &                    &            &         &\cellcolor{gray!75}&\cellcolor{gray!75}&                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&              &\\
    \multicolumn{1}{r|}{bet}  &                    &            &         &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&                   &                   &\cellcolor{gray!75}&              &\\      
    \multicolumn{1}{r|}{fast} &                    &            &         &\cellcolor{gray!75}&                   &                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&              &\\
    \multicolumn{1}{r|}{first}&                    &            &         &                   &                   &\cellcolor{gray!75}&\cellcolor{gray!75}&\cellcolor{gray!75}&                   &                   &              &\\
    FSL Nipype interfaces     \\
    HCP PreFreesurfer         &\cellcolor{gray!75} &            &         &                   &                   &                   &                   &                   &                   &                   &              &\\
    MSSEG MICCAI pipelines    \\
    PETSEG MICCAI pipelines   \\
\end{tabular}
\caption{Applications available in Boutiques with manifest features used.}
\label{table:applications}
  \end{table}
  \end{landscape}
